### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug

\begin{tabular}{llrrr}
\toprule
 &  & Mean & S.D. & N \\
\midrule
\multirow[c]{8}{*}{Panel A: Case Initiation} & For cause & 0.13 & 0.33 & 30, 505 \\
 & For cause; transferred from B.M.C. or D.C. & 0.01 & 0.09 & 30, 505 \\
 & Foreclosure & 0.02 & 0.15 & 30, 505 \\
 & Foreclosure; transferred from B.M.C. or D.C. & 0.00 & 0.03 & 30, 505 \\
 & No cause & 0.11 & 0.31 & 30, 505 \\
 & No cause; transferred from B.M.C. or D.C. & 0.01 & 0.08 & 30, 505 \\
 & Non-payment of rent & 0.71 & 0.46 & 30, 505 \\
 & Non-payment of rent; transferred from B.M.C. or D.C. & 0.02 & 0.13 & 30, 505 \\
\multirow[c]{5}{*}{Panel B: Case Resolution} & Case defaulted & 0.24 & 0.43 & 30, 505 \\
 & Case heard & 0.07 & 0.26 & 30, 505 \\
 & Case involuntarily dismissed & 0.12 & 0.33 & 30, 505 \\
 & Case mediated & 0.52 & 0.50 & 30, 505 \\
 & Case voluntarily dismissed & 0.00 & 0.00 & 30, 505 \\
\multirow[c]{5}{*}{Panel C: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.10 & 0.30 & 30, 505 \\
 & Defendant is an entity & 0.01 & 0.08 & 30, 505 \\
 & Money judgment & 4706.79 & 7661.71 & 15, 588 \\
 & Plaintiff has an attorney & 0.82 & 0.39 & 30, 505 \\
 & Plaintiff is an entity & 0.66 & 0.47 & 30, 505 \\
\multirow[c]{5}{*}{Panel C: Tax Assessment Records from F.Y. Following Eviction Filing} & Building value & 2007807.90 & 5532224.22 & 12, 089 \\
 & Land value & 99020.63 & 539763.97 & 12, 089 \\
 & Other value & 9827333.04 & 22977540.22 & 12, 089 \\
 & Total property value & 7731082.50 & 18211631.86 & 12, 089 \\
 & Total value & 39.15 & 113.83 & 12, 089 \\
\multirow[c]{9}{*}{Panel E: Zestimates Around Treatment} & Five years before latest docket date & 283010.66 & 265189.42 & 6, 848 \\
 & Four years before latest docket date & 305906.07 & 337719.48 & 6, 950 \\
 & Latest docket date & 435193.84 & 476324.79 & 6, 943 \\
 & One year after latest docket date & 474304.25 & 446024.13 & 4, 910 \\
 & One year before latest docket date & 395691.50 & 416306.93 & 7, 045 \\
 & Three years before latest docket date & 344030.70 & 1167207.98 & 6, 966 \\
 & Two years after latest docket date & 507403.55 & 1140138.35 & 2, 680 \\
 & Two years before latest docket date & 352784.42 & 300314.15 & 6, 992 \\
 & Units & 263662.99 & 223748.00 & 6, 766 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llrrr}
\toprule
 &  & Mean & S.D. & N \\
\midrule
\multirow[c]{8}{*}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30, 505 \\
 & For cause; transferred from B.M.C. or D.C. & 0.01 & 0.09 & 30, 505 \\
 & Foreclosure & 0.02 & 0.15 & 30, 505 \\
 & Foreclosure; transferred from B.M.C. or D.C. & 0.00 & 0.03 & 30, 505 \\
 & No cause & 0.11 & 0.31 & 30, 505 \\
 & No cause; transferred from B.M.C. or D.C. & 0.01 & 0.08 & 30, 505 \\
 & Non-payment of rent & 0.71 & 0.46 & 30, 505 \\
 & Non-payment of rent; transferred from B.M.C. or D.C. & 0.02 & 0.13 & 30, 505 \\
\cline{1-5}
\multirow[c]{5}{*}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.24 & 0.43 & 30, 505 \\
 & Case heard & 0.07 & 0.26 & 30, 505 \\
 & Case involuntarily dismissed & 0.12 & 0.33 & 30, 505 \\
 & Case mediated & 0.52 & 0.50 & 30, 505 \\
 & Case voluntarily dismissed & 0.00 & 0.00 & 30, 505 \\
\cline{1-5}
\multirow[c]{5}{*}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Building value & 2007807.90 & 5532224.22 & 12, 089 \\
 & Land value & 99020.63 & 539763.97 & 12, 089 \\
 & Other value & 9827333.04 & 22977540.22 & 12, 089 \\
 & Total property value & 7731082.50 & 18211631.86 & 12, 089 \\
 & Total value & 39.15 & 113.83 & 12, 089 \\
\cline{1-5}
\multirow[c]{5}{*}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.10 & 0.30 & 30, 505 \\
 & Defendant is an entity & 0.01 & 0.08 & 30, 505 \\
 & Money judgment & 4706.79 & 7661.71 & 15, 588 \\
 & Plaintiff has an attorney & 0.82 & 0.39 & 30, 505 \\
 & Plaintiff is an entity & 0.66 & 0.47 & 30, 505 \\
\cline{1-5}
\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 283010.66 & 265189.42 & 6, 848 \\
 & Four years before latest docket date & 305906.07 & 337719.48 & 6, 950 \\
 & Latest docket date & 435193.84 & 476324.79 & 6, 943 \\
 & One year after latest docket date & 474304.25 & 446024.13 & 4, 910 \\
 & One year before latest docket date & 395691.50 & 416306.93 & 7, 045 \\
 & Three years before latest docket date & 344030.70 & 1167207.98 & 6, 966 \\
 & Two years after latest docket date & 507403.55 & 1140138.35 & 2, 680 \\
 & Two years before latest docket date & 352784.42 & 300314.15 & 6, 992 \\
 & Units & 263662.99 & 223748.00 & 6, 766 \\
\cline{1-5}
\bottomrule
\end{tabular}
